---
title: "EDA"
author: "Süleyman Erim, Giacomo Schiavo, Mattia Varagnolo"
date: "`r Sys.Date()`"
output: pdf_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
``` 
# Introduction to data

```{r message=FALSE}
# import libraries
library(tidyverse)
library(corrplot)
library(ggplot2)
library(gridExtra)
library(correlation)
library(reshape)
library(reshape2)

data_train = read.csv("train.csv")
data_test = read.csv("test.csv")

# merge train and test data
data = rbind(data_train, data_test)
attach(data)
```
### VARIABLE DESCRIPTION
```{r}
# Print summary for each variable grouped by satisfaction, including the name of the variable
for (col in names(data)) {
  print(col)
  print(by(data[[col]], data$satisfaction, summary))
}
```

```{r}
# print names of the columns
names(data)
```

# DATA PREPROCESSING
Here we create factors from categorical variables
```{r}
# replace dots with underscores in column names
names(data) = gsub("\\.", "_", names(data))

# drop X and id column
data = data %>% select(-X, -id)

names(data)
```


```{r}
# convert categorical features to factor
data$Gender = factor(data$Gender, levels = c("Male", "Female"))
data$Customer_Type = factor(data$Customer_Type, levels = c("Loyal Customer", "disloyal Customer"))
data$Type_of_Travel = factor(data$Type_of_Travel, levels = c("Personal Travel", "Business travel"))
data$Class = factor(data$Class, levels = c("Business", "Eco Plus", "Eco"))
data$satisfaction = factor(data$satisfaction, levels = c("neutral or dissatisfied", "satisfied"))
```
# HANDLING NA VALUES
```{r}
# list features with na values
prop.table(colSums(is.na(data)))
```

From here we can see that Arrival_Delay_in_Minutes has missing values, let's the proportion of na values
```{r}
# Arrival_Delay_in_Minutes has na values, proportion of na values
prop.table(table(is.na(data$Arrival_Delay_in_Minutes)))

# na values are only 0.03% of the data -> drop na values
data = data %>% drop_na(Arrival_Delay_in_Minutes)
```
It turns out that Arrival_Delay_in_Minutes has only 3% of na values so we drop this examples.

### OUTLIERS
```{r fig.height=50}
# plot boxplot of numeric variables
plots = list()
for (col in names(data)[sapply(data, is.numeric)]) {
  plot = ggplot(data, aes(x = .data[[col]])) +
  geom_boxplot() +
  labs(title = col, x = col, y = "Count") 
  plots[[col]] = plot
}

grid.arrange(grobs = plots, ncol = 3)
```


```{r fig.height=20}
# plot boxplot against satisfaction with colors
plots = list()
for (col in names(data)[sapply(data, is.numeric)]) {
  plot = ggplot(data, aes(x = satisfaction, y = .data[[col]], fill = satisfaction)) +
  geom_boxplot() +
  labs(title = col, x = "Satisfaction", y = col) 
  plots[[col]] = plot
}

grid.arrange(grobs = plots, ncol = 2)
```


###   VISUALIZATION 
```{r}
# plot pie chart for each variable
plots = list()
for (col in names(data)[sapply(data, is.factor)]) {
  plot = ggplot(data, aes(x = "", fill = .data[[col]])) +
  geom_bar(width = 1) +
  coord_polar("y", start = 0) +
  labs(title = paste("Pie Chart of", col))
  plots[[col]] = plot
}

grid.arrange(grobs = plots, ncol = 3)
```


```{r}
# plot distribution of categorical variables
plots = list()
for (col in names(data)[sapply(data, is.factor)]) {
  plot = ggplot(data, aes(x = .data[[col]], fill = .data[[col]])) +
  geom_bar() +
  labs(title = paste("Histogram of", col), x = col, y = "Count")

  plots[[col]] = plot
}

grid.arrange(grobs = plots, ncol = 2)
```


```{r}
# plot distribution of numeric variables
plots = list()
for (col in names(data)[sapply(data, is.numeric)]) {
  plot = ggplot(data, aes(x = .data[[col]])) +
  geom_histogram(binwidth = 0.5) +
  labs(title = col, x = col, y = "Count") 
  plots[[col]] = plot
}

grid.arrange(grobs = plots, ncol = 3)
```


```{r}
# plots categorical variables vs satisfaction
plots = list()
for (col in names(data)[sapply(data, is.factor)]) {
  if (col == "satisfaction") {
    next
  }
  plot = ggplot(data, aes(x = satisfaction, fill = .data[[col]])) +
  geom_bar(position = "dodge") +
  scale_fill_manual(values = rainbow(length(unique(data[[col]]))), 
                    labels = unique(data[[col]]),
                    name = col) +
  labs(title = paste("Histogram of Satisfaction by", col), x = "Satisfaction", y = "Count")

  plots[[col]] = plot
  
}

grid.arrange(grobs = plots, ncol = 2)
```


```{r}
# Create density plots for Age and Flight_Distance
plots = list()
for (col in c("Age", "Flight_Distance")) {
  plot = ggplot(data, aes(x = .data[[col]], fill = satisfaction)) +
  geom_density(alpha = 0.4) +
  labs(title = paste("Density Plot of", col), x = col, y = "Density") 
  plots[[col]] = plot
}

# Arrange the density plots in a grid
grid.arrange(grobs = plots)

```


```{r}
# plots numeric variables vs satisfaction
plots = list()
for (col in names(data)[sapply(data, is.numeric)]) {
  if (col == "satisfaction") {
    next
  }
  plot = ggplot(data, aes(x = satisfaction, y = .data[[col]])) +
  geom_boxplot() +
  labs(x = "Satisfaction", y = col)

  plots[[col]] = plot
  
}

grid.arrange(grobs = plots, ncol = 4)
```


###   CONVERT CATEGORICAL TO NUMERIC
```{r}
data$Gender = as.numeric(data$Gender) - 1
data$Customer_Type = as.numeric(data$Customer_Type) - 1
data$Type_of_Travel = as.numeric(data$Type_of_Travel) - 1
data$Class = as.numeric(data$Class) - 1
data$satisfaction = as.numeric(data$satisfaction) - 1
```
###   DATA BALANCE
```{r}
prop.table(table(data$satisfaction))
```
###  TRAIN TEST SPLIT
```{r}
set.seed(123)
train_index = sample(1:nrow(data), 0.8*nrow(data))
# 80% of data is used for training
train = data[train_index,]
# 20% of data is used for testing
test = data[-train_index,]

# merge train and test data
data = rbind(train, test)
# save on cvs
# write.csv(data, "data.csv")

# save true values of test satisfaction column
test_true = test$satisfaction

# drop satisfaction column from test data
test = test %>% select(-satisfaction)

# print proportion of satisfied and dissatisfied customers in train and test data
prop.table(table(train$satisfaction))
prop.table(table(test_true))
```

### CORRELATION MATRIX
```{r}
# correlation matrix only for numeric variables
correlation_matrix = cor(data[, sapply(data, is.numeric)])

# Plot a heatmap of the correlation matrix
ggplot(data = reshape2::melt(correlation_matrix)) +
  geom_tile(aes(x = Var1, y = Var2, fill = value)) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0, limit = c(-1,1), space = "Lab",
                       name="Correlation") +
  theme(axis.text.x = element_text(angle = 90, vjust = 1, 
                                    size = 10, hjust = 1)) +
  coord_fixed()
```


```{r}
# Find high correlated features with satisfaction
# TODO: do the same with different threshold to find differences
# NOTE: i decided to use 0.3 as threshold
satisfaction_corr <- correlation_matrix['satisfaction',]
high_corr_satis <- names(satisfaction_corr[abs(satisfaction_corr) > 0.3 | abs(satisfaction_corr) < -0.3])
high_corr_satis <- high_corr_satis[high_corr_satis != "satisfaction"]
high_corr_satis
```


```{r}
# Compute the correlations between the high correlation features and satisfaction
correlations <- data.frame(
  feature = high_corr_satis,
  correlation = sapply(high_corr_satis, function(x) cor(data[,x], data$satisfaction))
)
correlations
```


```{r}
# plot the correlations
ggplot(correlations, aes(x = reorder(feature, correlation), y = correlation)) +
  geom_bar(stat = "identity", fill = "blue", alpha = 0.4) +
  ggtitle("Correlation between features and satisfaction") +
  xlab('Features') +
  ylab('Correlation')

par(mfrow = c(1, 1))
```


```{r}
#save on cvs
# write.csv(correlations, file = "correlations.csv")
```


### PLOT ALL DISTRIBUTIONS (with numerical categories)
```{r}

```

```{r}
sat <- data$satisfaction
features_names <- names(data)

num_cols <- 3
num_rows <- ceiling(length(features_names) / num_cols)

# Set smaller figure margins
par(mar = c(2, 2, 2, 2))  # Adjust the margin values as per your preference

# Loop through each feature and plot the density of satisfied and dissatisfied customers
for (col in features_names) {
  # Calculate the number of breaks
  num_breaks <- length(unique(data[[col]]))
  num_breaks <- min(num_breaks, 20) 
  
  # Create a new plot for each feature
  hist(data[[col]], breaks = num_breaks,
       main = paste("Histogram of", col), xlab = col, ylab = "Frequency",
       col = "lightblue"
  )
}

# Reset the plotting settings to default
par(mfrow = c(1, 1))

```


```{r}

a = ggplot(train, aes(x = Type_of_Travel, fill = sat)) +
  geom_bar(fill = 'Blue', alpha = 0.4) 


b = ggplot(train, aes(x = Class, fill = sat)) +
  geom_bar(fill = 'Blue', alpha = 0.4) +
  ggtitle("Class") +
  xlab('Class')

c = ggplot(train, aes(x = Online_boarding, fill = sat)) +
  geom_bar(fill = 'Blue', alpha = 0.4) +
  ggtitle("Online_boarding") +
  xlab('Online_boarding')

d = ggplot(train, aes(x = Seat_comfort, fill = sat)) +
  geom_bar(fill = 'Blue', alpha = 0.4) +
  ggtitle("Seat_comfort") +
  xlab('Seat_comfort')

e = ggplot(train, aes(x = Inflight_entertainment, fill = sat)) +
  geom_bar(fill = 'Blue', alpha = 0.4) +
  ggtitle("Inflight_entertainment") +
  xlab('Inflight_entertainment')

f = ggplot(train, aes(x = On_board_service, fill = sat)) +
  geom_bar(fill = 'Blue', alpha = 0.4) +
  ggtitle("On_board_service") +
  xlab('On_board_service')


g = ggplot(train, aes(x = Leg_room_service, fill = sat)) +
  geom_bar(fill = 'Blue', alpha = 0.4) +
  ggtitle("Leg_room_service") +
  xlab('Leg_room_service')

h = ggplot(train, aes(x = Cleanliness, fill = sat)) +
  geom_bar(fill = 'Blue', alpha = 0.4) +
  ggtitle("Cleanliness") +
  xlab('Cleanliness')


grid.arrange(a, b, c, d, e, f, g, h, ncol = 3)
```

### Relation between Arrival_Delay_in_Minutes and Departure_Delay_in_Minutes (linear)
```{r}

#CORRELATION MATRIX again but now we are interested in partial correlation
#So we look for all the correlations between variables
#We pick the highest, setting a treshold of our choice

#build a dataframe where for each variable we look the partial correlation with all the others
#we pick the highest and we save it in a dataframe
#we set a treshold of 0


#correlation(train, partial=TRUE, method='pearson')
#save the partial correlation matrix result in a dataframe and output a file for further analysis


#partial_corr <- correlation(train, partial=TRUE, method='pearson')
#write.csv(partial_corr, file = "partial_corr.csv")

partial_correlations = read.csv("partial_corr.csv", header = TRUE, sep = ",")

#make the first column the row names
rownames(partial_correlations) = partial_correlations[,1]

#drop the first  (X) column
partial_correlations = partial_correlations[,-1]

# Create a new matrix with rounded partial correlations
partial_correlations_rounded <- round(partial_correlations, digits = 3)


# Initialize empty data frame with 0 rows
# We need it to create a data frame with the results and
# so to show better the correlations.
df <- data.frame(variable1 = character(),
                 variable2 = character(),
                 value = numeric(),
                 stringsAsFactors = FALSE)

# Loop over rows and columns of matrix
for (i in 1:nrow(partial_correlations_rounded)) {
  for (j in 1:ncol(partial_correlations_rounded)) {
    # Check if value meets criterion
    if ((partial_correlations_rounded[i,j] > 0.300 | partial_correlations_rounded[i,j] < -0.300)& i != j) {
      # Add row to data frame
      df <- rbind(df, data.frame(variable1 = rownames(partial_correlations_rounded)[i],
                                 variable2 = colnames(partial_correlations_rounded)[j],
                                 value = partial_correlations_rounded[i,j],
                                 stringsAsFactors = FALSE))
    }
  }
}


# Group the data frame by variable1 and extract top 3 values for each group
df_top3 <- df %>% group_by(variable1) %>% top_n(4, value) %>% ungroup()

#order by variable1
df_top3 <- df_top3[order(df_top3$variable1),]


#delete duplicates in the dataframe if variable1 is equal to variable2
df_top3 <- df_top3[!(df_top3$variable1 == df_top3$variable2),]

print(df_top3, n = nrow(df_top3))
#save on cvs
# write.csv(df_top3, file = "df_top3.csv")
```

```{r}
# standardize Arrival_Delay_in_Minutes and Departure_Delay_in_Minutes
arrival_std = scale(data$Arrival_Delay_in_Minutes)
departure_std = scale(data$Departure_Delay_in_Minutes)
# scatter plot of Arrival_Delay_in_Minutes and Departure_Delay_in_Minutes 
plot(arrival_std, departure_std, xlab = "Arrival_Delay_in_Minutes", ylab = "Departure_Delay_in_Minutes")
# plot line y = x
abline(0, 1, col = "red")
```

```{r}
# print table of type of travel by satisfacton
table(data$Type_of_Travel, data$satisfaction)
```

```{r}

# select examples of departure delay greater than 500
examples=data[data$Departure_Delay_in_Minutes > 800,] 
# and print table of satisfaction by departure delay
table(examples$satisfaction)

# count the number of examples with departure delay = 0
sum(data$Departure_Delay_in_Minutes > 0)
sum(data$Departure_Delay_in_Minutes <= 0)

sum(data$Arrival_Delay_in_Minutes > 0)
sum(data$Arrival_Delay_in_Minutes <= 0)

summary(data)

```