---
title: "EDA"
author: "Süleyman Erim, Giacomo Schiavo, Mattia Varagnolo"
date: "`r Sys.Date()`"
output: pdf_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction to data

This section introduces the purpose of the exploratory data analysis
(EDA) and sets up the necessary libraries and data files.

```{r message=FALSE}
# import libraries
library(tidyverse)
library(corrplot)
library(ggplot2)
library(gridExtra)
library(correlation)
library(reshape)
library(reshape2)
```


```{r message=FALSE}
data_train = read.csv("train.csv")
data_test = read.csv("test.csv")

# merge train and test data
data = rbind(data_train, data_test)
attach(data)
```


# Introduction
In this project, we will predict whether a passenger will be satisfied or dissatisfied with the services offered by an airline company. The dataset comprises a survey on airline passenger satisfaction.

The main objectives of this project are to identify the factors that have a strong correlation with passenger satisfaction or dissatisfaction and to develop a predictive model for passenger satisfaction.

The dataset: https://www.kaggle.com/datasets/teejmahal20/airline-passenger-satisfaction


All the variables in the dataset are described below:
+ Gender: Gender of the passengers (Female, Male)
+ Customer Type: The customer type (Loyal customer, disloyal customer)
+ Age: The actual age of the passengers
+ Type of Travel: Purpose of the flight of the passengers (Personal Travel, Business Travel)
+ Class: Travel class in the plane of the passengers (Business, Eco, Eco Plus)
+ Flight distance: The flight distance of this journey
+ Inflight wifi service: Satisfaction level of the inflight wifi service (0:Not Applicable;1-5)
+ Departure/Arrival time convenient: Satisfaction level of Departure/Arrival time convenient
+ Ease of Online booking: Satisfaction level of online booking
+ Gate location: Satisfaction level of Gate location
+ Food and drink: Satisfaction level of Food and drink
+ Online boarding: Satisfaction level of online boarding
+ Seat comfort: Satisfaction level of Seat comfort
+ Inflight entertainment: Satisfaction level of inflight entertainment
+ On-board service: Satisfaction level of On-board service
+ Leg room service: Satisfaction level of Leg room service
+ Baggage handling: Satisfaction level of baggage handling
+ Check-in service: Satisfaction level of Check-in service
+ Inflight service: Satisfaction level of inflight service
+ Cleanliness: Satisfaction level of Cleanliness
+ Departure Delay in Minutes: Minutes delayed when departure
+ Arrival Delay in Minutes: Minutes delayed when Arrival
+ Satisfaction: Airline satisfaction level(Satisfaction, neutral or dissatisfaction)

The objective of our report is to predict passenger satisfaction with airline services based on the provided dataset, which includes various demographic and satisfaction-related variables such as gender, age, travel type, flight class, and satisfaction levels with different aspects of the journey. 
The dataset represents a survey on airline passenger satisfaction and will be used to develop a predictive model to determine whether passengers will be satisfied or dissatisfied with the airline services.

Now we're going to get a summary of all the features in our dataset:
```{r}
summary(data)
```

From the summary, it is evident that many features represent ratings on the services provided by the airline agency, and these ratings range from 0 to 5. Additionally, we noticed that the "Arrival Delay in Minutes" feature contains some missing values (NA).

Next, we will examine the distribution of all nominal features. Specifically, we have categorical data for Gender, Customer Type, Type of Travel, and Class, while all the rating features are ordinal.

```{r}
table(data$Gender)
```
The "Gender" feature appears to be well-balanced, meaning that it has an approximately equal number of occurrences for each category, likely male and female. This balance can be beneficial for modeling as it prevents any significant bias towards a particular gender in the analysis and predictions.

```{r}
table(data$Customer.Type)
```
The "Customer Type" feature contains only two values, "disloyal customer" and "loyal customer." The distribution of values is imbalanced, with one category potentially having significantly more occurrences than the other.
```{r}
table(data$Type.of.Travel)
```
The "Type of Travel" feature consists of only two values: "personal travel" and "business travel." The distribution of values is imbalanced, with "business travel" occurring twice as much as "personal travel."

```{r}
table(data$Class)
```
The "Class" feature contains three values: "business," "eco plus," and "eco." The distribution of values is imbalanced. "Business" and "eco" classes appear to be relatively balanced, while "eco plus" is significantly underrepresented compared to the other two classes.

```{r}
table(data$satisfaction)
```
The "satisfaction" feature, which serves as our target variable, is an important aspect of the analysis. The values for this feature are not perfectly balanced, meaning that there is an unequal distribution of satisfied and dissatisfied passengers in the dataset.

# Data preprocessing

In this section of data preprocessing, several steps are performed to prepare the dataset for further analysis and modeling. The specific actions taken include:

1. Renaming columns: the names of the features (columns) are modified to improve their clarity and usability. 

2. Dropping unnecessary columns: two columns, "X" and "id," are removed from the dataset. The "X" column likely represents the index of the row, which does not carry any meaningful information for analysis. The "id" column is presumed to be an unknown indexing number, which may not contribute to the predictive modeling process.

3. Converting categorical variables to factors: categorical variables, such as "Gender", "Customer Type", "Type of Travel" and "Class" are converted into factors. Converting categorical variables into factors is a common practice in R to represent these variables as distinct levels, allowing for better handling and analysis in statistical models.

By performing these data preprocessing steps, the dataset is cleaned and transformed into a more suitable format for the subsequent analysis, making it easier to build a predictive model for passenger satisfaction.

```{r}
# replace dots with underscores in column names
names(data) = gsub("\\.", "_", names(data))
# drop X and id column
data = data %>% select(-X, -id)
names(data)
```

```{r}
# convert categorical features to factor
data$Gender = factor(data$Gender, levels = c("Male", "Female"))
data$Customer_Type = factor(data$Customer_Type, levels = c("Loyal Customer", "disloyal Customer"))
data$Type_of_Travel = factor(data$Type_of_Travel, levels = c("Personal Travel", "Business travel"))
data$Class = factor(data$Class, levels = c("Business", "Eco Plus", "Eco"))
data$satisfaction = factor(data$satisfaction, levels = c("neutral or dissatisfied", "satisfied"))
```

# Handling na values

In this section, we analyze the dataset to identify variables with missing values, particularly focusing on the "Arrival_Delay_in_Minutes" variable. We calculate the proportion of missing values for this variable and subsequently remove the examples or rows with missing values from the dataset.

```{r}
# list features with na values
prop.table(colSums(is.na(data)))
```

To determine the proportion of missing values for the "Arrival_Delay_in_Minutes" variable, we can count the number of instances where this variable has missing values (commonly denoted as "NaN" or "NA") and divide it by the total number of examples in the dataset. This will give us the proportion of missing values for the "Arrival_Delay_in_Minutes" variable.

```{r}
# Arrival_Delay_in_Minutes has na values, proportion of na values
prop.table(table(is.na(data$Arrival_Delay_in_Minutes)))
```
Indeed, since the proportion of missing values for the "Arrival_Delay_in_Minutes" variable is very low (less than 3% of the entire dataset), it is reasonable to proceed with dropping these missing values from the dataset. 
```{r}
# na values are only 0.03% of the data -> drop na values
data = data %>% drop_na(Arrival_Delay_in_Minutes)
```

# Outliers

In this section, box plots are created for each numeric variable present in the dataset. Box plots are a powerful visualization tool used to identify the presence of outliers in the data. For each numeric variable, the box plot displays a box that represents the interquartile range (IQR), with the median indicated by a line inside the box. The "whiskers" extending from the box show the range of the data, and any data points beyond the whiskers are considered potential outliers.

By examining the box plots for each numeric variable, we can visually identify any data points that lie far outside the typical range of the data, indicating potential outliers. Outliers can significantly impact statistical analyses, so detecting and handling them appropriately is crucial for ensuring the integrity of the dataset and the accuracy of subsequent analyses and modeling.

```{r}
ratings_fts_names = c("Inflight_wifi_service", "Departure_Arrival_time_convenient", 
  "Ease_of_Online_booking", "Gate_location", "Food_and_drink", "Online_boarding", 
  "Seat_comfort", "Inflight_entertainment", "On_board_service", "Leg_room_service", 
  "Baggage_handling", "Checkin_service", "Inflight_service", "Cleanliness", "On_board_service")

# plot boxplot of each numeric variable excluding ratings features
plots = list()
for (col in names(data)[sapply(data, is.numeric)]) {
  if (col %in% ratings_fts_names) {
    next
  }
  plot = ggplot(data, aes(x = .data[[col]])) +
  geom_boxplot() +
  labs(title = col, x = col, y = "Count") 
  plots[[col]] = plot
}

grid.arrange(grobs = plots, ncol = 2)
```
We can see that there are outliers in Departure_Delay_in_Minutes, Arrival_Delay_in_Minutes and Flight_Distance.
Considering the presence of both near-zero and very large values in the dataset, alternative distributions like the log-normal distribution may be more appropriate for modeling the "Departure_Delay_in_Minutes" and "Arrival_Delay_in_Minutes" variables, as they can better capture the variability in delay times.

# Our variables vs satisfaction

Now we can visualize how the features are distributed by satisfaction.
This section provides a summary of each variable in the dataset, grouped
by our target variable.

```{r}
# Print summary for each variable grouped by satisfaction, including the name of the variable
for (col in names(data)) {
  print(col)
  print(by(data[[col]], data$satisfaction, summary))
}
```
From the analysis of the dataset, we observe the following insights:

1. Gender does not appear to significantly influence satisfaction levels, as both men and women show similar satisfaction and dissatisfaction rates.

2. There is a trend suggesting that younger passengers are more likely to be dissatisfied compared to older passengers, as evidenced by the lower values at the 1st quartile and median of the age distribution for dissatisfied customers.

3. Passengers traveling for personal reasons are more likely to be dissatisfied than those on business trips.

4. Conversely, passengers on business trips have a slightly higher likelihood of being satisfied with their travel experience.

5. Customers in the business class are more likely to be satisfied with the airline services compared to those in the economy and economy plus classes.

6. Longer distance flights tend to have higher satisfaction levels among passengers.

7. Departure and arrival delays are associated with a higher likelihood of passenger dissatisfaction.

These insights provide valuable information for the airline company to understand customer preferences and pain points, allowing them to improve services, prioritize customer satisfaction, and address specific areas that may lead to dissatisfaction among passengers.
Visualizing each distribution can indeed provide a clearer understanding of the results.

# Visualization

In this section, histograms are used to visualize the distribution of the variables in the dataset, starting with the nominal features. By creating histograms for the nominal features, we can gain insights into the distribution of categories within each feature.

Upon visualizing the nominal features, it becomes apparent that some features exhibit heavily unbalanced distributions. This means that certain categories within these features have significantly higher frequencies compared to others. The presence of such imbalanced distributions could have implications for analysis and modeling, as it may lead to biased results or difficulties in predicting less frequent categories accurately.

```{r fig.height=10, fig.width=12}
# plot distribution of categorical variables
plots = list()
for (col in names(data)[sapply(data, is.factor)]) {
  plot = ggplot(data, aes(x = .data[[col]], fill = .data[[col]])) +
  geom_bar() +
  labs(title = paste("Histogram of", col), x = col, y = "Count") +
  guides(fill = FALSE)

  plots[[col]] = plot
}

grid.arrange(grobs = plots, ncol = 2)
```

Then we plot the distribution of ratings features.

```{r fig.height=18, fig.width=12}
# plot distribution of ratings features
plots = list()
my_palette <- c("#1f78b4", "#33a02c", "#e31a1c", "#ff7f00", "#6a3d9a", "#b15928")

for (col in names(data)[sapply(data, is.numeric)]) {
  if (!col %in% ratings_fts_names) {
    next
  }
  plot <- ggplot(data, aes(x = .data[[col]], fill = factor(.data[[col]]))) +
    geom_bar() +
    geom_text(stat = 'count', aes(label = after_stat(count))) +  
    labs(title = paste("Histogram of ", col), x = col, y = "Count") +
    scale_fill_manual(values = my_palette) +
    guides(fill = FALSE)

  plots[[col]] <- plot
}
grid.arrange(grobs = plots, ncol = 3)
```

This section includes histograms to visualize the distribution of
numeric variables in the dataset.

**needs interpretation **

```{r}
# plot distribution and density of numeric variables excluding ratings features
plots = list()
for (col in names(data)[sapply(data, is.numeric)]) {
  if (col %in% ratings_fts_names) {
    next
  }
  plot = ggplot(data, aes(x = .data[[col]])) +
  geom_histogram(aes(y = after_stat(density)), bins = 30, alpha = 0.5) +
  geom_density(alpha = 0.2, fill = "red") +
  labs(title = paste("Histogram of", col), x = col, y = "Count") 

  plots[[col]] = plot
}

grid.arrange(grobs = plots, ncol = 2)
```

# Visualization vs satisfaction

** TODO: write interpretations of the graphs **

```{r fig.width=12}
# plots categorical variables vs satisfaction
plots = list()
for (col in names(data)[sapply(data, is.factor)]) {
  if (col == "satisfaction") {
    next
  }
  plot = ggplot(data, aes(x = satisfaction, fill = .data[[col]])) +
  theme_minimal() +
  geom_bar(position = "dodge") +
  labs(title = paste("Histogram of Satisfaction by", col), x = "Satisfaction", y = "Count")

  plots[[col]] = plot
  
}

grid.arrange(grobs = plots, ncol = 2)
```

```{r fig.height=28, fig.width=12}
# plots ratings features vs satisfaction
plots = list()
for (col in names(data)[sapply(data, is.numeric)]) {
  if (!col %in% ratings_fts_names) {
    next
  }
  plot = ggplot(data, aes(x = .data[[col]], fill = satisfaction)) +
  theme_minimal() +
  geom_bar(position = "dodge") +
  labs(title = paste("Histogram of Satisfaction by", col), x = "Satisfaction", y = "Count")

  plots[[col]] = plot  
}

grid.arrange(grobs = plots, ncol = 2)
```

```{r fig.height=10, fig.width=10}
# plots numeric variables vs satisfaction excluding ratings features
plots = list()

for (col in names(data)[sapply(data, is.numeric)]) {
  if (col %in% ratings_fts_names) {
    next
  }
  plot = ggplot(data, aes(x = satisfaction, y = .data[[col]])) +
  theme_minimal() +
  geom_boxplot() +
  labs(title = paste("Boxplot of Satisfaction by", col), x = "Satisfaction", y = col)

  plots[[col]] = plot  
}

grid.arrange(grobs = plots, ncol = 2)

```

# Convert categorical to numerical

This section converts the categorical variables to numeric
representation for further analysis.

```{r}
gender_map = c("Male" = 0, "Female" = 1)
data$Gender = gender_map[as.numeric(data$Gender)]

customer_type_map = c("Loyal Customer" = 0, "disloyal Customer" = 1)
data$Customer_Type = customer_type_map[as.numeric(data$Customer_Type)]

type_of_travel_map = c("Personal Travel" = 0, "Business travel" = 1)
data$Type_of_Travel = type_of_travel_map[as.numeric(data$Type_of_Travel)]

class_map = c("Business" = 0, "Eco" = 1, "Eco Plus" = 2)
data$Class = class_map[as.numeric(data$Class)]
```


```{r}
satisfaction_map = c("neutral or dissatisfied" = 0, "satisfied" = 1)
data$satisfaction = satisfaction_map[as.numeric(data$satisfaction)]
```

# Data balance

This section calculates the proportion of satisfied and dissatisfied
customers in the dataset.

```{r}
prop.table(table(data$satisfaction))
```

# Train test split

This section splits the data into training and testing sets, prints the
proportion of satisfied and dissatisfied customers in each set, and
saves the true values of the target variable for the test set.

```{r}
set.seed(123)
train_index = sample(1:nrow(data), 0.8*nrow(data))
# 80% of data is used for training
train = data[train_index,]
# 20% of data is used for testing
test = data[-train_index,]

# merge train and test data
data = rbind(train, test)
# save on cvs
# write.csv(data, "data.csv")

# save true values of test satisfaction column
test_true = test$satisfaction

# drop satisfaction column from test data
test = test %>% select(-satisfaction)

# print proportion of satisfied and dissatisfied customers in train and test data
prop.table(table(train$satisfaction))
prop.table(table(test_true))
```

# Correlation matrix

This section calculates the correlation matrix for numeric variables and
plots a heatmap to visualize the correlations between variables.

```{r fig.height=12, fig.width=12}
# correlation matrix only for numeric variables
correlation_matrix = cor(data[, sapply(data, is.numeric)])

# Plot a heatmap of the correlation matrix
ggplot(data = reshape2::melt(correlation_matrix)) +
  geom_tile(aes(x = Var1, y = Var2, fill = value)) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0, limit = c(-1,1), space = "Lab",
                       name="Correlation") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, 
                                    size = 10, hjust = 1)) +
  coord_fixed()

par(mfrow = c(1, 1))
```

```{r}
# Find high correlated features with satisfaction
# TODO: do the same with different threshold to find differences
# NOTE: i decided to use 0.3 as threshold
satisfaction_corr <- correlation_matrix['satisfaction',]
high_corr_satis <- names(satisfaction_corr[abs(satisfaction_corr) > 0.3 | abs(satisfaction_corr) < -0.3])
high_corr_satis <- high_corr_satis[high_corr_satis != "satisfaction"]
high_corr_satis
```

```{r}
# Compute the correlations between the high correlation features and satisfaction
correlations <- data.frame(
  feature = high_corr_satis,
  correlation = sapply(high_corr_satis, function(x) cor(data[,x], data$satisfaction))
)
correlations
```

```{r}
# plot the correlations
ggplot(correlations, aes(x = reorder(feature, correlation), y = correlation)) +
  geom_bar(stat = "identity", fill = "blue", alpha = 0.4) +
  ggtitle("Correlation between features and satisfaction") +
  xlab('Features') +
  ylab('Correlation')

par(mfrow = c(1, 1))
```

```{r}
#save on cvs
# write.csv(correlations, file = "correlations.csv")
```

# Correlation with different ratings

```{r fig.height=8, fig.width=8}
# compute correlation matrix with only ratings features
ratings_data = data[, c(ratings_fts_names)]

# correlation matrix only for ratings features
ratings_correlation_matrix = cor(ratings_data)

# Plot a heatmap of the correlation matrix
ggplot(data = reshape2::melt(ratings_correlation_matrix)) +
  geom_tile(aes(x = Var1, y = Var2, fill = value)) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0, limit = c(-1,1), space = "Lab",
                       name="Correlation") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, 
                                    size = 10, hjust = 1)) +
  coord_fixed()

par(mfrow = c(1, 1))

```
```{r}
# Assuming you have already calculated the 'ratings_correlation_matrix' using the code you provided.

# Convert the correlation matrix to a data frame to work with it easily
ratings_correlation_df <- as.data.frame(as.table(ratings_correlation_matrix))

# Rename the columns in the data frame
colnames(ratings_correlation_df) <- c("Var1", "Var2", "Correlation")

# Sort the data frame by the absolute correlation values in descending order
sorted_correlation_df <- ratings_correlation_df[order(-abs(ratings_correlation_df$Correlation)), ]

# Filter out the self-correlations (correlation of a variable with itself)
sorted_correlation_df <- sorted_correlation_df[sorted_correlation_df$Var1 != sorted_correlation_df$Var2, ]

# Print the top N most correlated features
N <- 15  # Change N to get more or fewer correlated features
top_correlated_features <- head(sorted_correlation_df, N)

print(top_correlated_features)

```


# Relation between Arrival_Delay_in_Minutes and Departure_Delay_in_Minutes (linear)

This section explores the partial correlation matrix and identifies
variables with high correlations with the target variable
(satisfaction). It also creates a bar plot to show the correlations.

```{r}

#CORRELATION MATRIX again but now we are interested in partial correlation
#So we look for all the correlations between variables
#We pick the highest, setting a treshold of our choice

#build a dataframe where for each variable we look the partial correlation with all the others
#we pick the highest and we save it in a dataframe
#we set a treshold of 0


#correlation(train, partial=TRUE, method='pearson')
#save the partial correlation matrix result in a dataframe and output a file for further analysis


#partial_corr <- correlation(train, partial=TRUE, method='pearson')
#write.csv(partial_corr, file = "partial_corr.csv")

partial_correlations = read.csv("partial_corr.csv", header = TRUE, sep = ",")

#make the first column the row names
rownames(partial_correlations) = partial_correlations[,1]

#drop the first  (X) column
partial_correlations = partial_correlations[,-1]

# Create a new matrix with rounded partial correlations
partial_correlations_rounded <- round(partial_correlations, digits = 3)


# Initialize empty data frame with 0 rows
# We need it to create a data frame with the results and
# so to show better the correlations.
df <- data.frame(variable1 = character(),
                 variable2 = character(),
                 value = numeric(),
                 stringsAsFactors = FALSE)

# Loop over rows and columns of matrix
for (i in 1:nrow(partial_correlations_rounded)) {
  for (j in 1:ncol(partial_correlations_rounded)) {
    # Check if value meets criterion
    if ((partial_correlations_rounded[i,j] > 0.300 | partial_correlations_rounded[i,j] < -0.300)& i != j) {
      # Add row to data frame
      df <- rbind(df, data.frame(variable1 = rownames(partial_correlations_rounded)[i],
                                 variable2 = colnames(partial_correlations_rounded)[j],
                                 value = partial_correlations_rounded[i,j],
                                 stringsAsFactors = FALSE))
    }
  }
}


# Group the data frame by variable1 and extract top 3 values for each group
df_top3 <- df %>% group_by(variable1) %>% top_n(4, value) %>% ungroup()

#order by variable1
df_top3 <- df_top3[order(df_top3$variable1),]


#delete duplicates in the dataframe if variable1 is equal to variable2
df_top3 <- df_top3[!(df_top3$variable1 == df_top3$variable2),]

print(df_top3, n = nrow(df_top3))
#save on cvs
# write.csv(df_top3, file = "df_top3.csv")
```

```{r}
# standardize Arrival_Delay_in_Minutes and Departure_Delay_in_Minutes
arrival_std = scale(data$Arrival_Delay_in_Minutes)
departure_std = scale(data$Departure_Delay_in_Minutes)
# scatter plot of Arrival_Delay_in_Minutes and Departure_Delay_in_Minutes 
plot(arrival_std, departure_std, xlab = "Arrival_Delay_in_Minutes", ylab = "Departure_Delay_in_Minutes")
# plot line y = x
abline(0, 1, col = "red")
```


