---
title: "EDA"
author: "Süleyman Erim, Giacomo Schiavo, Mattia Varagnolo"
date: "`r Sys.Date()`"
output: pdf_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction to data

This section introduces the purpose of the exploratory data analysis
(EDA) and sets up the necessary libraries and data files.

```{r message=FALSE}
# import libraries
library(tidyverse)
library(corrplot)
library(ggplot2)
library(gridExtra)
library(correlation)
library(reshape)
library(reshape2)
```


```{r message=FALSE}
data_train = read.csv("train.csv")
data_test = read.csv("test.csv")

# merge train and test data
data = rbind(data_train, data_test)
attach(data)
```


# Introduction
In this project, we will predict whether a passenger will be satisfied or dissatisfied with the services offered by an airline company. The dataset comprises a survey on airline passenger satisfaction.

The main objectives of this project are to identify the factors that have a strong correlation with passenger satisfaction or dissatisfaction and to develop a predictive model for passenger satisfaction.

The dataset: https://www.kaggle.com/datasets/teejmahal20/airline-passenger-satisfaction

```{r}
summary(data)
```

From the summary we can see that a lot of features are ordinal because they represent ratings for different services offered during a flight. 
We can observe that some NA values are present in "Arrival.Delay.in.Minutes" feature, it will be dealt later.
Now we will look into all the nominal features to see their primal distribution.

```{r}
table(data$Gender)
```
"Gender" feature is quite perfectly balanced.

```{r}
table(data$Customer.Type)
```
We can see that in Customer.Type feature there are only two values, disloyal and loyal customer. 
The values for this feature are not balanced, we will see later if this feature is useful for our model.

```{r}
table(data$Type.of.Travel)
```
Also in Type.of.Travel feature there are only two values, personal and business travel.
The values for this feature are not balanced, business travel are double than personal travel.

```{r}
table(data$Class)
```
In Class feature there are three values, business, eco plus and eco.
The values for this feature are not balanced, business and eco looks quite balanced while eco plus is way more less represented.

```{r}
table(data$satisfaction)
```
Our target feature is satisfaction, we can see that the values are not perfectly balanced. 

# Data preprocessing

This section performs data preprocessing steps such as renaming columns,
dropping unnecessary columns, and converting categorical variables to
factors.

```{r}
# replace dots with underscores in column names
names(data) = gsub("\\.", "_", names(data))
# drop X and id column
data = data %>% select(-X, -id)
names(data)
```

```{r}
# convert categorical features to factor
data$Gender = factor(data$Gender, levels = c("Male", "Female"))
data$Customer_Type = factor(data$Customer_Type, levels = c("Loyal Customer", "disloyal Customer"))
data$Type_of_Travel = factor(data$Type_of_Travel, levels = c("Personal Travel", "Business travel"))
data$Class = factor(data$Class, levels = c("Business", "Eco Plus", "Eco"))
data$satisfaction = factor(data$satisfaction, levels = c("neutral or dissatisfied", "satisfied"))
```

Now we can visualize how the features are distributed by satisfaction.
This section provides a summary of each variable in the dataset, grouped
by our target variable.

```{r}
# Print summary for each variable grouped by satisfaction, including the name of the variable
for (col in names(data)) {
  print(col)
  print(by(data[[col]], data$satisfaction, summary))
}
```
From here we can see that:
+ men and women are equally satisfied and dissatisfied
+ dissatisfied customer are younger than satisfied customer (see 1st quartile and median)
+ personal travel is more likely to be dissatisfied than business travel
+ business travel are slightly more likely to be satisfied 
+ business class' customers are more likely to be satisfied than eco and eco plus
+ longer distance flights are more likely to be satisfied
+ departure and arrival delays are more likely to bring dissatisfaction


# Handling na values

This section identifies the variables with missing values and calculates
the proportion of missing values for the "Arrival_Delay_in_Minutes"
variable. It then drops the examples with missing values.

```{r}
# list features with na values
prop.table(colSums(is.na(data)))
```

From here we can see that Arrival_Delay_in_Minutes has missing values,
let's the proportion of na values

```{r}
# Arrival_Delay_in_Minutes has na values, proportion of na values
prop.table(table(is.na(data$Arrival_Delay_in_Minutes)))
```
We can see that the proportion of na values is very low (less than 3% of the entire dataset), we can drop the na values.

```{r}
# na values are only 0.03% of the data -> drop na values
data = data %>% drop_na(Arrival_Delay_in_Minutes)
```

# Outliers

This section creates box plots for each numeric variable in the dataset
to visualize the presence of outliers. It also compares the box plots
against the target variable (satisfaction).

```{r}
ratings_fts_names = c("Inflight_wifi_service", "Departure_Arrival_time_convenient", 
  "Ease_of_Online_booking", "Gate_location", "Food_and_drink", "Online_boarding", 
  "Seat_comfort", "Inflight_entertainment", "On_board_service", "Leg_room_service", 
  "Baggage_handling", "Checkin_service", "Inflight_service", "Cleanliness", "On_board_service")
# plot boxplot of each numeric variable excluding ratings features
plots = list()
for (col in names(data)[sapply(data, is.numeric)]) {
  if (col %in% ratings_fts_names) {
    next
  }
  plot = ggplot(data, aes(x = .data[[col]])) +
  geom_boxplot() +
  labs(title = col, x = col, y = "Count") 
  plots[[col]] = plot
}

grid.arrange(grobs = plots, ncol = 2)
```
We can see that there are outliers in Departure_Delay_in_Minutes, Arrival_Delay_in_Minutes and Flight_Distance.

# Visualization

This section includes histograms to visualize the distribution of
categorical variables in the dataset.

```{r fig.height=10, fig.width=12}
# plot distribution of categorical variables
plots = list()
for (col in names(data)[sapply(data, is.factor)]) {
  plot = ggplot(data, aes(x = .data[[col]], fill = .data[[col]])) +
  geom_bar() +
  labs(title = paste("Histogram of", col), x = col, y = "Count") +
  guides(fill = FALSE)

  plots[[col]] = plot
}

grid.arrange(grobs = plots, ncol = 2)
```

Here we plot the distribution of ratings features.
```{r fig.height=18, fig.width=12}
# plot distribution of ratings features
plots = list()
my_palette <- c("#1f78b4", "#33a02c", "#e31a1c", "#ff7f00", "#6a3d9a", "#b15928")

for (col in names(data)[sapply(data, is.numeric)]) {
  if (!col %in% ratings_fts_names) {
    next
  }
  plot <- ggplot(data, aes(x = .data[[col]], fill = factor(.data[[col]]))) +
    geom_bar() +
    geom_text(stat = 'count', aes(label = ..count..), vjust = -0.5) +  
    labs(title = paste("Histogram of ", col), x = col, y = "Count") +
    scale_fill_manual(values = my_palette) +
    guides(fill = FALSE)

  plots[[col]] <- plot
}
grid.arrange(grobs = plots, ncol = 3)
```



```{r}
plots <- list()
for (col in names(data)[sapply(data, is.numeric)]) {
  if (!col %in% ratings_fts_names) {
    next
  }
  plot <- ggplot(data, aes(x = .data[[col]], fill = factor(.data[[col]]))) +
    geom_bar() +
    geom_text(stat = 'count', aes(label = ..count..), vjust = -0.5) +  # Add count labels below each bar
    labs(title = paste("Histogram of ", col), x = col, y = "Count", bins = 6) +
    scale_fill_manual(values = my_palette) +  # Adding the custom color palette
    facet_grid(. ~ satisfaction)  # Separate the plots based on 'satisfaction'

  plots[[col]] <- plot
}

# Adjust the heights of the plots using 'heights' argument in grid.arrange
grid.arrange(grobs = plots, ncol = 3)

```

This section includes histograms to visualize the distribution of
numeric variables in the dataset.

```{r}
# plot distribution and density of numeric variables excluding ratings features
plots = list()
for (col in names(data)[sapply(data, is.numeric)]) {
  if (col %in% ratings_fts_names) {
    next
  }
  plot = ggplot(data, aes(x = .data[[col]])) +
  geom_histogram(aes(y = after_stat(density)), bins = 30, alpha = 0.5) +
  geom_density(alpha = 0.5, fill = "red") +
  labs(title = paste("Histogram of", col), x = col, y = "Count") 

  plots[[col]] = plot
}

grid.arrange(grobs = plots, ncol = 2)
```

```{r}
# plots categorical variables vs satisfaction
plots = list()
for (col in names(data)[sapply(data, is.factor)]) {
  if (col == "satisfaction") {
    next
  }
  plot = ggplot(data, aes(x = satisfaction, fill = .data[[col]])) +
  theme_minimal() +
  geom_bar(position = "dodge") +
  labs(title = paste("Histogram of Satisfaction by", col), x = "Satisfaction", y = "Count")

  plots[[col]] = plot
  
}

grid.arrange(grobs = plots, ncol = 2)
```

```{r}
# plots ratings features vs satisfaction
plots = list()
for (col in names(data)[sapply(data, is.numeric)]) {
  if (!col %in% ratings_fts_names) {
    next
  }
  plot = ggplot(data, aes(x = .data[[col]], fill = satisfaction)) +
  theme_minimal() +
  geom_bar(position = "dodge") +
  labs(title = paste("Histogram of Satisfaction by", col), x = "Satisfaction", y = "Count")

  plots[[col]] = plot  
}

grid.arrange(grobs = plots, ncol = 3)
```

```{r fig.height=10}
# plots numeric variables vs satisfaction
plots = list()
for (col in names(data)[sapply(data, is.numeric)]) {
  if (col == "satisfaction") {
    next
  }
  plot = ggplot(data, aes(x = satisfaction, y = .data[[col]])) +
  geom_boxplot() +
  labs(x = "Satisfaction", y = col)

  plots[[col]] = plot
  
}

grid.arrange(grobs = plots, ncol = 4)
```

# Convert categorical to numerical

This section converts the categorical variables to numeric
representation for further analysis.

```{r}
gender_map = c("Male" = 0, "Female" = 1)
data$Gender = gender_map[as.numeric(data$Gender)]

customer_type_map = c("Loyal Customer" = 0, "disloyal Customer" = 1)
data$Customer_Type = customer_type_map[as.numeric(data$Customer_Type)]

type_of_travel_map = c("Personal Travel" = 0, "Business travel" = 1)
data$Type_of_Travel = type_of_travel_map[as.numeric(data$Type_of_Travel)]

class_map = c("Business" = 0, "Eco" = 1, "Eco Plus" = 2)
data$Class = class_map[as.numeric(data$Class)]
```


```{r}
satisfaction_map = c("neutral or dissatisfied" = 0, "satisfied" = 1)
data$satisfaction = satisfaction_map[as.numeric(data$satisfaction)]
```

# Data balance

This section calculates the proportion of satisfied and dissatisfied
customers in the dataset.

```{r}
prop.table(table(data$satisfaction))
```

# Train test split

This section splits the data into training and testing sets, prints the
proportion of satisfied and dissatisfied customers in each set, and
saves the true values of the target variable for the test set.

```{r}
set.seed(123)
train_index = sample(1:nrow(data), 0.8*nrow(data))
# 80% of data is used for training
train = data[train_index,]
# 20% of data is used for testing
test = data[-train_index,]

# merge train and test data
data = rbind(train, test)
# save on cvs
# write.csv(data, "data.csv")

# save true values of test satisfaction column
test_true = test$satisfaction

# drop satisfaction column from test data
test = test %>% select(-satisfaction)

# print proportion of satisfied and dissatisfied customers in train and test data
prop.table(table(train$satisfaction))
prop.table(table(test_true))
```

# Correlation matrix

This section calculates the correlation matrix for numeric variables and
plots a heatmap to visualize the correlations between variables.

```{r fig.height=12, fig.width=12}
# correlation matrix only for numeric variables
correlation_matrix = cor(data[, sapply(data, is.numeric)])

# Plot a heatmap of the correlation matrix
ggplot(data = reshape2::melt(correlation_matrix)) +
  geom_tile(aes(x = Var1, y = Var2, fill = value)) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0, limit = c(-1,1), space = "Lab",
                       name="Correlation") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, 
                                    size = 10, hjust = 1)) +
  coord_fixed()

par(mfrow = c(1, 1))
```

```{r}
# Find high correlated features with satisfaction
# TODO: do the same with different threshold to find differences
# NOTE: i decided to use 0.3 as threshold
satisfaction_corr <- correlation_matrix['satisfaction',]
high_corr_satis <- names(satisfaction_corr[abs(satisfaction_corr) > 0.3 | abs(satisfaction_corr) < -0.3])
high_corr_satis <- high_corr_satis[high_corr_satis != "satisfaction"]
high_corr_satis
```

```{r}
# Compute the correlations between the high correlation features and satisfaction
correlations <- data.frame(
  feature = high_corr_satis,
  correlation = sapply(high_corr_satis, function(x) cor(data[,x], data$satisfaction))
)
correlations
```

```{r}
# plot the correlations
ggplot(correlations, aes(x = reorder(feature, correlation), y = correlation)) +
  geom_bar(stat = "identity", fill = "blue", alpha = 0.4) +
  ggtitle("Correlation between features and satisfaction") +
  xlab('Features') +
  ylab('Correlation')

par(mfrow = c(1, 1))
```

```{r}
#save on cvs
# write.csv(correlations, file = "correlations.csv")
```

# Correlation with different ratings

```{r fig.height=8, fig.width=8}
# compute correlation matrix with only ratings features
ratings_data = data[, c(ratings_fts_names)]

# correlation matrix only for ratings features
ratings_correlation_matrix = cor(ratings_data)

# Plot a heatmap of the correlation matrix
ggplot(data = reshape2::melt(ratings_correlation_matrix)) +
  geom_tile(aes(x = Var1, y = Var2, fill = value)) +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 0, limit = c(-1,1), space = "Lab",
                       name="Correlation") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, 
                                    size = 10, hjust = 1)) +
  coord_fixed()

par(mfrow = c(1, 1))

```
```{r}
# Assuming you have already calculated the 'ratings_correlation_matrix' using the code you provided.

# Convert the correlation matrix to a data frame to work with it easily
ratings_correlation_df <- as.data.frame(as.table(ratings_correlation_matrix))

# Rename the columns in the data frame
colnames(ratings_correlation_df) <- c("Var1", "Var2", "Correlation")

# Sort the data frame by the absolute correlation values in descending order
sorted_correlation_df <- ratings_correlation_df[order(-abs(ratings_correlation_df$Correlation)), ]

# Filter out the self-correlations (correlation of a variable with itself)
sorted_correlation_df <- sorted_correlation_df[sorted_correlation_df$Var1 != sorted_correlation_df$Var2, ]

# Print the top N most correlated features
N <- 15  # Change N to get more or fewer correlated features
top_correlated_features <- head(sorted_correlation_df, N)

print(top_correlated_features)

```


# Relation between Arrival_Delay_in_Minutes and Departure_Delay_in_Minutes (linear)

This section explores the partial correlation matrix and identifies
variables with high correlations with the target variable
(satisfaction). It also creates a bar plot to show the correlations.

```{r}

#CORRELATION MATRIX again but now we are interested in partial correlation
#So we look for all the correlations between variables
#We pick the highest, setting a treshold of our choice

#build a dataframe where for each variable we look the partial correlation with all the others
#we pick the highest and we save it in a dataframe
#we set a treshold of 0


#correlation(train, partial=TRUE, method='pearson')
#save the partial correlation matrix result in a dataframe and output a file for further analysis


#partial_corr <- correlation(train, partial=TRUE, method='pearson')
#write.csv(partial_corr, file = "partial_corr.csv")

partial_correlations = read.csv("partial_corr.csv", header = TRUE, sep = ",")

#make the first column the row names
rownames(partial_correlations) = partial_correlations[,1]

#drop the first  (X) column
partial_correlations = partial_correlations[,-1]

# Create a new matrix with rounded partial correlations
partial_correlations_rounded <- round(partial_correlations, digits = 3)


# Initialize empty data frame with 0 rows
# We need it to create a data frame with the results and
# so to show better the correlations.
df <- data.frame(variable1 = character(),
                 variable2 = character(),
                 value = numeric(),
                 stringsAsFactors = FALSE)

# Loop over rows and columns of matrix
for (i in 1:nrow(partial_correlations_rounded)) {
  for (j in 1:ncol(partial_correlations_rounded)) {
    # Check if value meets criterion
    if ((partial_correlations_rounded[i,j] > 0.300 | partial_correlations_rounded[i,j] < -0.300)& i != j) {
      # Add row to data frame
      df <- rbind(df, data.frame(variable1 = rownames(partial_correlations_rounded)[i],
                                 variable2 = colnames(partial_correlations_rounded)[j],
                                 value = partial_correlations_rounded[i,j],
                                 stringsAsFactors = FALSE))
    }
  }
}


# Group the data frame by variable1 and extract top 3 values for each group
df_top3 <- df %>% group_by(variable1) %>% top_n(4, value) %>% ungroup()

#order by variable1
df_top3 <- df_top3[order(df_top3$variable1),]


#delete duplicates in the dataframe if variable1 is equal to variable2
df_top3 <- df_top3[!(df_top3$variable1 == df_top3$variable2),]

print(df_top3, n = nrow(df_top3))
#save on cvs
# write.csv(df_top3, file = "df_top3.csv")
```

```{r}
# standardize Arrival_Delay_in_Minutes and Departure_Delay_in_Minutes
arrival_std = scale(data$Arrival_Delay_in_Minutes)
departure_std = scale(data$Departure_Delay_in_Minutes)
# scatter plot of Arrival_Delay_in_Minutes and Departure_Delay_in_Minutes 
plot(arrival_std, departure_std, xlab = "Arrival_Delay_in_Minutes", ylab = "Departure_Delay_in_Minutes")
# plot line y = x
abline(0, 1, col = "red")
```


